### 2021-09-03 README.Rmd
update the data, analysis and text with biobliometrics
update readme

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

@@

The **analysis** directory contains:

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

@@

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh///master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/systematicsinprehistory/master?urlpath=rstudio)

@@

The most important parts of this compendium are:

-   [:dart: \_targets.R](_targets.R): workflow instructions and
    information indicating the order that code needs to be run to
    generate the results. Run `targets::tar_make()` at the R console to
  start the analysis workflow.    
  - [:file\_folder: analysis/paper](/analysis/paper): R Markdown source document
    for manuscript, and R script files. Includes code to reproduce the figures and
    tables generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: analysis/data](/analysis/data): Data used in the analysis.
  - [:file\_folder: analysis/figures](/analysis/figures): Plots and other
    illustrations

@@

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/benmarwick/systematicsinprehistory/master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping you can run our code by followinfg these steps:

1. open the `.Rproj` file in RStudio      
2. run `renv::restore()` to download and install the packages required to run our code     
3. run `targets::tar_make()` to run our code in order, the final step of this will be 
 knitting the R Markdown document to produce the `paper.docx`
